\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-21 main.Rmd
added AFL

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. As a variant of boxplots, letter value plots represent each pair of adjacent letter values using one box, instead of whiskers. Figure \ref{fig:dow} demonstrates three letter values and outliers marked as asterisks, with a line representing the median (thus M) and the innermost boxes corresponding to the fourth (F) and the eighth quantiles (E). Household 3, with a family size of one couple and two kids, uses more energy over the weekdays given the medians, compared to the others consisting of one or two people. Whereas, household 2 displays a great deal of variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy on average with increased variations during the weekends relative to the weekdays, as a reflection of work and leisure patterns.

```{r dow, fig.height = 7, fig.cap = "Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the weekdays, due to a large family size. By constrast, household 2 sees considerally large variability."}
```

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between weekdays and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 6pm on weekdays. Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting weekdays and weekends for each household. All have different daily routines between weekdays and weekends, except for household 3. On weekdays, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2."}
```

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their weekday energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

>>>>

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. As a variant of boxplots, letter value plots represent each pair of adjacent letter values using one box, instead of whiskers. Figure \ref{fig:dow} demonstrates three letter values and outliers marked as asterisks, with a line representing the median (thus M) and the innermost boxes corresponding to the fourth (F) and the eighth quantiles (E). Household 3, with a family size of one couple and two kids, uses more energy over the week days given the medians, compared to the others consisting of one or two people. Whereas, household 2 displays a great deal of variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy on average with increased variations during the weekends relative to the week days, as a reflection of work and leisure patterns.

```{r dow, fig.height = 7, fig.cap = "Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability."}
```

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between week days and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days. Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2."}
```

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

### 2018-10-21 main.tex
added AFL

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the weekdays given the medians, compared to the others consisting of one
or two people. Whereas, household 2 displays a great deal of variability
in daily energy consumption with noticeable variations on Thursdays, and
much higher usage over the weekends. The other two households (1 and 4)
tend to consume more energy on average with increased variations during
the weekends relative to the weekdays, as a reflection of work and
leisure patterns.

@@

\caption{Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the weekdays, due to a large family size. By constrast, household 2 sees considerally large variability.}\label{fig:dow}
\end{figure}

Figure \ref{fig:hod} provides a more detailed depiction of each
household's life style, by plotting energy consumption against time of
day between weekdays and weekends. Household 1 is an early bird,
starting their day before 6 and going back home around 18 on weekdays.
They switch air conditioning or heating on when they get home from work
and keep it operated till mid-night, while learned from the tiny cluster
of points below 1 kWh. On the other hand, the strips above 1 kWh tells
that household 2 perhaps have air conditioning or heating on all time
during the days, consuming the energy almost as double as household 1.
Apart from the morning and night peak use, a third peak occurs around
3pm for household 3 only, when the kids are home from school. They also
share a consistent energy pattern between weekdays and weekends. As for
household 4, their home routine starts after 6pm on weekdays. Figure
\ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits,
are useful for summarizing overall deviations across days and
households.

@@

\caption{Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting weekdays and weekends for each household. All have different daily routines between weekdays and weekends, except for household 3. On weekdays, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2.}\label{fig:hod}
\end{figure}

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays
individually for each household, unfolding their day-to-day life.
Glancing through Figure \ref{fig:h12}, their weekday energy use
distinguishes from their weekends. We can exactly tell when their air
conditioner and heater are turned on. Heating keeps functioning in
consecutive hours at household 2, which is evident in the mid July;
while household 1 uses them cautiously. This finding helps explain the
strips and clusters in Figure \ref{fig:hod}. The calendar plots speak
the stories about vacation time that are untold by previous figures.
Household 1 is on vacation over three weeks of June, and household 2 was
also away for holidays during Christmas and the second week of June.
Figure \ref{fig:h34} shows household 3 takes two one-month-long family
trips in September till early October and in June/July, and household 4
is away over two or three weeks in early October, December and late
June. The use of air conditioning and heating leaves no trace in these
two households.

>>>>

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the week days given the medians, compared to the others consisting of
one or two people. Whereas, household 2 displays a great deal of
variability in daily energy consumption with noticeable variations on
Thursdays, and much higher usage over the weekends. The other two
households (1 and 4) tend to consume more energy on average with
increased variations during the weekends relative to the week days, as a
reflection of work and leisure patterns.

@@

\caption{Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability.}\label{fig:dow}
\end{figure}

Figure \ref{fig:hod} provides a more detailed depiction of each
household's life style, by plotting energy consumption against time of
day between week days and weekends. Household 1 is an early bird,
starting their day before 6 and going back home around 18 on week days.
They switch air conditioning or heating on when they get home from work
and keep it operated till mid-night, while learned from the tiny cluster
of points below 1 kWh. On the other hand, the strips above 1 kWh tells
that household 2 perhaps have air conditioning or heating on all time
during the days, consuming the energy almost as double as household 1.
Apart from the morning and night peak use, a third peak occurs around
3pm for household 3 only, when the kids are home from school. They also
share a consistent energy pattern between week days and weekends. As for
household 4, their home routine starts after 6pm on week days. Figure
\ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits,
are useful for summarizing overall deviations across days and
households.

@@

\caption{Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2.}\label{fig:hod}
\end{figure}

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays
individually for each household, unfolding their day-to-day life.
Glancing through Figure \ref{fig:h12}, their week day energy use
distinguishes from their weekends. We can exactly tell when their air
conditioner and heater are turned on. Heating keeps functioning in
consecutive hours at household 2, which is evident in the mid July;
while household 1 uses them cautiously. This finding helps explain the
strips and clusters in Figure \ref{fig:hod}. The calendar plots speak
the stories about vacation time that are untold by previous figures.
Household 1 is on vacation over three weeks of June, and household 2 was
also away for holidays during Christmas and the second week of June.
Figure \ref{fig:h34} shows household 3 takes two one-month-long family
trips in September till early October and in June/July, and household 4
is away over two or three weeks in early October, December and late
June. The use of air conditioning and heating leaves no trace in these
two households.
